Generating Datasets about Building Designs \\Based on a Multilayer Building Ontology

### 2015-05-01 article-02-main.tex
Version 2.0 (final)

\subsubsection{Data Section} includes entities, each of which is identified with a line number.
%, an entity data\-type and a list of values. 
All entities of \name{Ifc\-Root}-derived types have a GUID in IFC. They are converted into URI resources with format \name{GUID\_\emph{\textless{}guid\textgreater{}}} where \emph{guid} is in the hexadecimal string representation (not including the character \name{\$}). Regarding to anonymous IFC entities, it can be chosen whether to export them as blank nodes or create them a URI in a format \name{LINE\_\emph{\textless{}lineNumber\textgreater{}}} (in a user defined namespace). Note that line numbers are used only for linking entities inside a SPF, and they are unstable. Naming is required when the dataset is used together with OWL 2 EL/QL as these profiles do not allow anonymous individuals. Below is an example of IFC data exported to an RDF dataset compatible with OWL 2 RL:

@@

\begin{table}
    \caption{Contents of ifcOWL layers}
    \label{tab:ifc2ld-web}
    \centering
    \scriptsize
    \def\arraystretch{1.2}          % vertical space
    \setlength{\tabcolsep}{6pt}     % horizontal space
    \begin{tabularx}{0.90\textwidth}{|l|X|}
        \hline
        Ontologies: & \texttt{http://drumbeat.cs.hut.fi/owl/} \\
        \hline
        Example files & \\
        - IFC data: & \texttt{http://drumbeat.cs.hut.fi/ifc/} \\
        - RDF datasets: & \texttt{http://drumbeat.cs.hut.fi/rdf/} \\
        \hline
        IFC2LD Converter & \\
        - online service: & \texttt{http://drumbeat.cs.hut.fi/home/} \\
        - download binary: & \texttt{http://drumbeat.cs.hut.fi/ifc2ld/} \\
        % - source code: & \texttt{https://github.com/Web-of-Building-Data/Ifc2Rdf} \\
        \hline
    \end{tabularx}
\end{table}

>>>>

\subsubsection{Data Section} includes entities, each of which is identified with a line number.
%, an entity data\-type and a list of values. 
All entities of \name{Ifc\-Root}-derived types have a GUID in IFC. They are converted into URI resources with format \name{GUID\_\emph{\textless{}guid\textgreater{}}}; where \emph{guid} is in the hexadecimal string representation (not including the character \name{\$}). Regarding to anonymous IFC entities, it can be chosen whether to export them as blank nodes or create them a URI in a format \name{LINE\_\emph{\textless{}lineNumber\textgreater{}}} (in a user defined namespace). Note that line numbers are used only for linking entities inside a SPF, and they are unstable. Naming is required when the dataset is used together with OWL 2 EL/QL as these profiles do not allow anonymous individuals. Below is an example of IFC data exported to an RDF dataset compatible with OWL 2 RL:

@@

\begin{table}[b]
    \caption{Internet links to the related research results}
    \label{tab:ifc2ld-web}
    \centering
    \scriptsize
    \def\arraystretch{1.2}          % vertical space
    \setlength{\tabcolsep}{6pt}     % horizontal space
    \begin{tabularx}{0.90\textwidth}{|l|X|}
        \hline
        Ontologies: & \texttt{http://drumbeat.cs.hut.fi/owl/} \\
        \hline
        Example files & \\
        - IFC data: & \texttt{http://drumbeat.cs.hut.fi/ifc/} \\
        - RDF datasets: & \texttt{http://drumbeat.cs.hut.fi/rdf/} \\
        \hline
        IFC2LD Converter & \\
        - online service: & \texttt{http://drumbeat.cs.hut.fi/home/} \\
        - download binary: & \texttt{http://drumbeat.cs.hut.fi/ifc2ld/} \\
        % - source code: & \texttt{https://github.com/Web-of-Building-Data/Ifc2Rdf} \\
        \hline
    \end{tabularx}
\end{table}
